Wrangling coral and macroalgae data to be joinable

### 2024-08-15 julianna_algalMetric_wrangling.Rmd
Fixed CSV names to match Noam's for max reproducibility and took coral/sand out of algal metric datasheets

```{r calculate beta dispersion}
yrBetaDisperFring <- vegan::betadisper(brayMatFring, sppMeta0fring$year) # warning: some squared distances are negative and changed to zero (ask Jamie about this??)
```

@@

```{r calculate beta dispersion}
yrBetaDisperBack <- vegan::betadisper(brayMatBack, sppMeta0back$year) 
```

@@

```{r calculate beta dispersion}
yrBetaDisperOuter10 <- vegan::betadisper(brayMatOuter10, sppMeta0outer10$year) # error: some squared distances are negative and changed to zero
```

@@

```{r calculate beta dispersion}
yrBetaDisperOuter17 <- vegan::betadisper(brayMatOuter17, sppMeta0outer17$year) # error: some squared distances are negative and changed to zero
```

@@

```{r save}
# write_csv(quadData, here("data/algal_metrics_quadrat.csv"))
```

@@

```{r save dataframe}
# write_csv(siteData, here("data/algal_metrics_site.csv"))
```

@@

```{r save}
write_csv(alltimeJoin, here(here("data/algal_metrics_all_time.csv")))
```

>>>>

```{r calculate beta dispersion}
# yrBetaDisperFring <- vegan::betadisper(brayMatFring, sppMeta0fring$year) # warning: some squared distances are negative and changed to zero (ask Jamie about this??)
```

@@

```{r calculate beta dispersion}
# yrBetaDisperBack <- vegan::betadisper(brayMatBack, sppMeta0back$year) 
```

@@

```{r calculate beta dispersion}
# yrBetaDisperOuter10 <- vegan::betadisper(brayMatOuter10, sppMeta0outer10$year) # error: some squared distances are negative and changed to zero
```

@@

```{r calculate beta dispersion}
# yrBetaDisperOuter17 <- vegan::betadisper(brayMatOuter17, sppMeta0outer17$year) # error: some squared distances are negative and changed to zero
```

@@

```{r save}
write_csv(quadData, here("data/algae_diversity_quadrat.csv"))
```

@@

```{r save dataframe}
write_csv(siteData, here("data/algae_diversity_site.csv"))
```

@@

```{r save}
write_csv(alltimeJoin, here(here("data/algae_diversity_stability_metrics_alltime.csv")))
```

### 2024-08-15 julianna_coral_macroalg_wrangling.Rmd
Fixed CSV names to match Noam's for max reproducibility and took coral/sand out of algal metric datasheets

```{r calculate beta dispersion}
yrBetaDisperFringMacro <- vegan::betadisper(brayMatFringMacro, sppMeta0fring$year) # warning: some squared distances are negative and changed to zero (ask Jamie about this??)
```

@@

```{r calculate beta dispersion}
yrBetaDisperBackMacro <- vegan::betadisper(brayMatBackMacro, sppMeta0back$year) 
```

@@

```{r calculate beta dispersion}
yrBetaDisperOuter10Macro <- vegan::betadisper(brayMatOuter10Macro, sppMeta0outer10$year) # error: some squared distances are negative and changed to zero
```

@@

```{r calculate beta dispersion}
yrBetaDisperOuter17Macro <- vegan::betadisper(brayMatOuter17Macro, sppMeta0outer17$year) # error: some squared distances are negative and changed to zero
```

@@

```{r save}
# write_csv(quadData, here("data/macroalgal_metrics_quadrat.csv"))
```

@@

```{r save dataframe}
# write_csv(siteData, here("data/macroalgal_metrics_site.csv"))
```

@@

```{r save}
write_csv(alltimeCV, here(here("data/macroalgal_metrics_all_time.csv")))
```

>>>>

```{r calculate beta dispersion}
# yrBetaDisperFringMacro <- vegan::betadisper(brayMatFringMacro, sppMeta0fring$year) # warning: some squared distances are negative and changed to zero (ask Jamie about this??)
```

@@

```{r calculate beta dispersion}
# yrBetaDisperBackMacro <- vegan::betadisper(brayMatBackMacro, sppMeta0back$year) 
```

@@

```{r calculate beta dispersion}
# yrBetaDisperOuter10Macro <- vegan::betadisper(brayMatOuter10Macro, sppMeta0outer10$year) # error: some squared distances are negative and changed to zero
```

@@

```{r calculate beta dispersion}
# yrBetaDisperOuter17Macro <- vegan::betadisper(brayMatOuter17Macro, sppMeta0outer17$year) # error: some squared distances are negative and changed to zero
```

@@

```{r save}
 write_csv(quadData, here("data/macroalgae_diversity_quadrat.csv"))
```

@@

```{r save dataframe}
 write_csv(siteData, here("data/macroalgae_diversity_site.csv"))
```

@@

```{r save}
write_csv(alltimeCV, here(here("data/macroalgae_stability_metrics_all_time.csv")))
```
